Maxwell: bringing cloud-powered electromagnetic simulations to Matlab

### 2012-10-22 presentations/maxwell_documentation/pres.tex
More stuffs...

\oursection{How Maxwell solves electromagnetics}
\BIT
\I  In this section we detail the simulation parameters used by the 
    \verb+maxwell.solve()+ and \verb+maxwell.solve_async()+ functions
\EIT

>>>>

\oursection{How Maxwell solves electromagnetics}
\BIT
\I  In this section we detail the simulation parameters used by the 
    \verb+maxwell.solve()+ and \verb+maxwell.solve_async()+ functions
\I  Along with the \verb+'cluster-name'+ and \verb+n+ parameters, both
    functions support the following parameters which describe the physical simulation:
    \BIT
    \I  \verb+omega+
    \I  \verb+d_prim, d_dual, s_prim, s_dual+
    \I  \verb+mu, epsilon+
    \I  \verb+E, J+
    \I  \verb+max_iters, err_thresh+
    \EIT
    and can be understood from the master equation:
    \BEQ
    \nabla \times \mu^{-1} \nabla \times E - \omega^2 \epsilon E = -i \omega J
    \EEQ

\newpage
\I  Frequency parameter: \verb+omega+
\I  Spatial grid parameters: \verb+d_prim, d_dual, s_prim, s_dual+
\I  Material parameters: \verb+mu, epsilon+
\I  Field parameters: \verb+E, J+
\I  Convergence parameters: \verb+max_iters, err_thresh+
%  [E, H, err] = fds(omega, d_prim, d_dual, s_prim, s_dual, mu, epsilon, E, J, max_iters, err_thresh, view_progress)
\EIT
